Deep Reinforcement Learning for Conservation Decisions

### 2021-06-04 appendices/appendix-C-environments.Rmd

In Deep Reinforcement Learning (RL), and _environment_ is a mathematical model, computer simulation, or real world situation with which the agent interacts.
Defining an _environment_  requires 5 components:

1. Describe the states defining the environment
2. Describe the possible actions available to the agent
3. Update it's internal _state_ in response to the _action_ of the _agent_
4. Provide the agent with an _observation_ of the new state 
5. Provide the agent with a _reward_ based on the its state and the agent's action.

@@

This corresponds to the formal definition of a Partially Observed Markov Decision Process (POMDP), see main text and Appendix A.

>>>>

In Deep Reinforcement Learning (DRL), an _environment_ is a mathematical model, computer simulation, or real world situation with which the agent interacts.
Defining an _environment_  requires 5 components:

1. Describe the states defining the environment
2. Describe the possible actions available to the agent
3. Update the environment's internal _state_ in response to the _action_ of the _agent_
4. Provide the agent with an _observation_ of the new state 
5. Provide the agent with a _reward_ based on the environment's state and the agent's action.

@@

This corresponds to the formal definition of a Partially Observed Markov Decision Process (POMDP), see main text.

### 2021-06-04 manuscript/manuscript.Rmd
Small edit to the comment on fig1

\begin{figure}
\includegraphics[width=\linewidth]{fig1.pdf}
\caption{Deep Reinforcement Learning:  A deep RL \emph{agent} uses a \emph{neural network} to select an \emph{action} in response to an \emph{observation} of the \emph{environment}, and receives a \emph{reward} from the environment as a result. During \emph{training}, the agent tries to maximize its cumulative reward by interacting with the environment and learning from experience. In the RL loop, the agent performs an action, and the environment returns a reward as well as an observation of the environment's state. The agent-environment loop continues until the environment reaches a terminal state, after which the environment will reset, causing a new \emph{episode} to begin. Across training episodes, the agent will continually update the \emph{parameters} in its neural network, so that the agent will select better actions. Before training starts, the researcher must input a set of \emph{hyperparameters} to the agent; hyperparameters direct the learning process and thus affect the outcome of training. A researcher finds the best set of hyperparameters during \emph{tuning}. Hyperparameter tuning consists of iterative \emph{trials}, in which the agent is trained with different sets of hyperparameters. At the end of a trial, the agent is evaluated to see which agent attains the highest cumulative reward. An agent is \emph{evaluated} by recording the cumulative reward over one episode, or the mean reward over multiple episodes. Within evaluation, the agent does not update its neural network; instead, the agent only uses the neural network to select actions.}
\end{figure}

@@

<!-- ML: Need to rework this to talk about other environments that we are working on basically point to conservation gym website -->
One feature that most distinguishes RL from other approaches to decision theory (such as optimal control) is it's flexibility or ambition.
While optimal control approaches typically require extensive simplifying assumptions such as discrete states or actions, deterministic dynamics or short time horizons, RL is scoped more ambitiously.
Large, complex problems are still immensely challenging to RL, and existing RL approaches will frequently struggle to solve problems that can already be solved much more efficiently by other means.
Nevertheless, deep RL approaches using neural network architectures have proven successful on problems that no amount of computational power would put into reach of purely conventional methods.
Our previous examples have focused on relatively simple examples that can also be addressed at least approximately by conventional methods, and also permit RL-based solutions to be found relatively efficiently on commodity hardware.
To better illustrate the generality of RL approach and more typical complexity of conservation problems, we now introduce a third example for which we have not yet found an effective policy using RL or classical methods.

>>>>

\begin{figure}
\includegraphics[width=\linewidth]{fig1.pdf}
\caption{Deep Reinforcement Learning:  A deep RL \emph{agent} uses a \emph{neural network} to select an \emph{action} in response to an \emph{observation} of the \emph{environment}, and receives a \emph{reward} from the environment as a result. During \emph{training}, the agent tries to maximize its cumulative reward by interacting with the environment and learning from experience. In the RL loop, the agent performs an action, and the environment returns a reward as well as an observation of the environment's state. The agent-environment loop continues until the environment reaches a terminal state, after which the environment will reset, causing a new \emph{episode} to begin. Across training episodes, the agent will continually update the \emph{parameters} in its neural network, so that the agent will select better actions. Before training starts, the researcher must input a set of \emph{hyperparameters} to the agent; hyperparameters direct the learning process and thus affect the outcome of training. A researcher finds the best set of hyperparameters during \emph{tuning}. Hyperparameter tuning consists of iterative \emph{trials}, in which the agent is trained with different sets of hyperparameters. At the end of a trial, the agent is evaluated to see which set of hyperparameters results in the highest cumulative reward. An agent is \emph{evaluated} by recording the cumulative reward over one episode, or the mean reward over multiple episodes. Within evaluation, the agent does not update its neural network; instead, the agent only uses the neural network to select actions.}
\end{figure}

@@

One feature that most distinguishes deep RL from other approaches to decision theory (such as optimal control) is its flexibility and scope.
While optimal control approaches typically require extensive simplifying assumptions such as discrete states or actions, deterministic dynamics or short time horizons, deep RL is scoped more ambitiously.
Large, complex problems are still challenging to RL, and existing RL approaches can easily struggle to solve problems that can already be solved much more efficiently by other means.
Nevertheless, deep RL approaches have proven successful on problems that classical approaches could not solve despite immense computational resources -- e.g. deep RL  [@DQN, @alphago].
Our previous examples have focused on relatively simple problems that can also be addressed at least approximately by conventional methods, and also permit RL-based solutions to be found relatively efficiently on commodity hardware.
Yet, we also have developed
